---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Build Status](https://travis-ci.org/vincenzocoia/powers.svg?branch=master)](https://travis-ci.org/vincenzocoia/powers)


# powers

This is an R package that gives `square`, `cube`, `reciprocal`, `root_square` and `lm_plot` functions.

## Installation

You can install powers from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("hw07-lh563/powers")
```

## Example

See the vignette for more extensive use, but here's an example:

```{r example}
powers::reciprocal(2)
powers::square(1:10)
library(gapminder)
lmfun(gapminder$lifeExp, gapminder$gdpPercap, mydata = gapminder)
```

## For Developers

Use the internal `pow` function as the machinery for the front-end functions such as `square`, `cube`, `reciprocal`, `root_square` and `lm_plot`
